visualFields 1.0.7

### 2025-05-11 gallery/gallery.Rmd

---
title: visualFields 1.x
author:
  - Cord Huchzermeyer, Department of Ophthalmology, University Hospital Erlangen
  - Iván Marín-Franch, Computational Optometry
date: "`r Sys.Date()`"
output:   
  distill::distill_article:
    theme: styles.css
---

@@

example1 <- vffilter(vfpwgSunyiu24d2, 
                     id == "sample1" & 
                       eye == "OD")[1, ]

@@

@@

@@

@@

[Back](#plotting-single-fields)

>>>>

---
title: visualFields 1.0.7
author:
  - Cord Huchzermeyer, Department of Ophthalmology, University Hospital Erlangen
  - Iván Marín-Franch, Computational Optometry
date: "`r Sys.Date()`"
output:   
  distill::distill_article:
    theme: styles.css
---

@@

@@

*Please klick on the thumbnails to see more detail.*

@@

*Scroll down or click for ["plotting progression"](#plotting-progression).*

@@

*Scroll up or click or ["plotting single fields"](#plotting-single-fields).*

---

@@

[**Back to single fields**](#plotting-single-fields)
<br>
[**Back to progression**](#plotting-progression)
